\documentclass[journal,12pt,onecolumn,draftclsnofoot]{IEEEtran}  % Comment this line out
                                                          % if you need a4paper
% \documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper
\IEEEcompsocthanksitem
\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
% \overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\usepackage{subcaption}
% \captionsetup{compatibility=false}
% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{balance}
\usepackage[font=small,labelfont=bf]{caption} % makes figure captions small, and figure labels bold
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage[autostyle]{csquotes}  %makes block quotes possible
\usepackage{float} %insures proper placement of figures

\title{Classifying and Localizing Epileptic Brain States Using Structural Features of Neuronal Sugihara Causation Networks}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}
% \author{
%     \IEEEauthorblockN{Kamal Kamalaldin\IEEEauthorrefmark{1}, Rory Lewis\IEEEauthorrefmark{2}, Chad Mellow\IEEEauthorrefmark{2}, Dorottya R. Cserpán\IEEEauthorrefmark{3}, Somogyvári Zoltán\IEEEauthorrefmark{3}, Peter Erdi\IEEEauthorrefmark{1}{3}}
%     \IEEEauthorblockA{\IEEEauthorrefmark{1}Kalamazoo College
%     \\\kamal.aldin.94@gmail.com
%     \\\perdi@kzoo.edu}
%     \IEEEauthorblockA{\IEEEauthorrefmark{2}Institution2
%     \\\{2, 3\}@def.com}
% }

% \author{Kamal Kamalaldin, Rory Lewis, Chad Mellow, Dorottya R. Cserpán, Somogyvári Zoltán, Peter Erdi \\
% Kalamazoo College \footnote{Kamalaldin studies Computer Science and Mathematics at Kalamazoo College, 1200 Academy St, Kalamazoo, MI 49006. He is also participating in the REU with the Department of Computer Science, University of Coloardo Colorado Springs.}}

\author{
    \IEEEauthorblockN{Kamal Kamalaldin\IEEEauthorrefmark{1}, Rory Lewis\IEEEauthorrefmark{2}, Chad Mello\IEEEauthorrefmark{2}, Dorottya R. Cserpán\IEEEauthorrefmark{3}, Somogyvári Zoltán\IEEEauthorrefmark{3}, Peter Erdi\IEEEauthorrefmark{1}\IEEEauthorrefmark{3}, Zsolt Borhegyi\IEEEauthorrefmark{4}}
    \\~\\
    \IEEEauthorblockA{\IEEEauthorrefmark{1}Kalamazoo College, MI}
    \\\IEEEauthorblockA{\IEEEauthorrefmark{2}University of Colorado Colorado Springs}
    \\\IEEEauthorblockA{\IEEEauthorrefmark{3}Wigner RCP, Budapest}
    \\\IEEEauthorblockA{\IEEEauthorrefmark{4}MTA-TKI , MTA-ELTE-NAP B-Opto-Neuropharmacology Group}
}

\usepackage{neuralnetwork}
\begin{document}

\maketitle

\thispagestyle{empty}
\cleardoublepage

\tableofcontents

\thispagestyle{empty}
\cleardoublepage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Epilepsy is a brain disease that profoundly affects the personal lives of its patients as well as the health care system needed to address it. Machine learning is a field of computer science experiencing a renaissance period at a time where computers can do more work in less time than ever before. While industry has moved rapidly towards  implementation of machine learning in profitable and futuristic endeavors like autonomous driving and image recognition and creation, some basic and essential societal problems remain relatively unexamined through the lens of machine learning research, an example of which is epilepsy. This work attempts to start to fill this gap and shed light on the ways machine learning can address complex and intricate problems like epilepsy. Through it, several machine learning algorithms will be surveyed, and some simple implementations and tutorials be provided through an external companion. Furthermore, a novel definition of brain communication is introduced in the form of causality, which will also be discussed more broadly. This definition is then used to construct a network of brain communication patterns in the context of which the author attempts to apply machine learning. Finally, discoveries made in this work will highlight a lack of a general understanding and framework of brain communication patterns and the magnitude and scope of future work available in the intersection of neuroscience and machine learning.
\end{abstract}
% \begin{abstract}
% \centering
% OLD ABSTRACT \\
% Causality is a topic of philosophical and technical debate in scientific fields relating to multivariate systems. Sugihara Causality is a new model for describing causality. We investigate how this model can be applied to highly dimensional neuronal networks where epilepsy is induced. Different brain states will be classified using a neuroclustering algorithm. The time indecies of the clustered brain states will be used to discretize the original EEG signal into different epileptic seizures stages. A causality network will be created for each stage from the discretized EEG signal, and analysis on the network will be conducted to find predictive structural patterns in epileptic seizures.

% \end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \include{outline}
\include{introdution}
\clearpage
\input{Epilepsy}
\clearpage
\input{history_of_machine_learning}
\input{supervised_learning}
\input{unsupervised_learning}
% \include{reinforcement_learning}
\include{Sugihara}
\include{Experiment}
\section{Conclusion}
The paper shows promising initial results using the Sugihara CCM model to construct causality graphs between brain regions. We find that the brain network for this experiment is highly causal with a range of time windows. This, however, could be due in part to experimental design limitations, where the electrodes were 1 mm apart which might have caused electrical interference. To to limit this phenomenon we used kCSD to preprocess the data. Initial results show a time varying graph in which information flow can be tracked. At the moment, more analysis is required to make a conclusions on the capabilities of the pairwise causality graph model. Some of most incurring difficulties to overcome are the running complexity of the kCSD preprocessing and CCM algorithm required for the analysis of the amount of pairs in a large network, and the mathematical representation of information flow within the time-dependent graph. We plan on using the Neuroclustering algorithm to discretize the EEG data into epileptic seizures, extract causal network features from the stages, and train a k-means learning algorithm on the created feature set. The implications of these findings could relate more generally to discoverability of causality in modeling scalable natural phenomena. Real world applications manifest in localization of epilepsy in the brain. Furthermore, if the technique of distinguishing causal networks in systems and clustering their properties is successful, it could be a clear indications that the Sugihara causality model is able to detect causation in extremely complex systems comparable to the human brain.

\section*{Acknowledgment}

Special thanks goes to Dr. Somogivari and Dorrottya R. from Winger RCP, Budapest for providing the neuronal data used in this paper. Furthermore, Dr. Peter Erdi is thanked for his patient guidance of this research topic which was instrumental for the production of this paper.

\balance
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,main.bib}
\end{document}
